---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# iotr

<!-- badges: start -->
[![R-CMD-check](https://github.com/okrebs/iotr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/okrebs/iotr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview

Package for working with Input Output Tables in quantitative economics.

Download and convert I-O-data from different sources. 

Currently supported databases:

- OECD's ICIO v2 (see OECD 2023):
    - download tables
    - convert to standardized long format

- OECD's ICIO (see OECD 2021):
    - download tables
    - convert to standardized long format

- WIOD (see Timmer et al. 2015):
    - download tables
    - convert to standardized long format

Planned support:

- Eora
- USITC ITPD-IO
- Eurostat
    
Additional functionality (possibly outsourced/removed in the future):

- remove 'dynamic' demand categories, e.g. inventory or GFCF, following the 
method proposed in Costino and Rodríguez-Clare (2014)

- remove entries with negative value added from and IO-table by scaling demand

- remove entries where exports but no "own trade" exists by replacing them with
small entries

References: 
- OECD (2023) OECD Inter-Country Input-Output Tables. http://oe.cd/icio

- OECD (2021). OECD Inter-Country Input-Output Database. http://oe.cd/icio

- Timmer, Marcel P., Dietzenbacher, Erik, Los, Bart, Stehrer, Robert and de
Vries, Gaaitzen J. (2015). An Illustrated User Guide to the World Input–Output
Database: the Case of Global Automotive Production. Review of International
Economics, 23: 575–605.

- Costinot, Arnaud and Rodríguez-Clare, Andrés (2014). Trade Theory
with Numbers: Quantifying the Consequences of Globalization. Handbook of 
International Economics, 4:197:261.

## Installation

<!-- You can install the released version of iotr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("iotr")
``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("okrebs/iotr")
```

Early development version, all functionality is subject to change!

## Examples

See "man/examples/wiod.R", "man/examples/icio.R", and "man/examples/icio_v2.R

```{r example}
library(iotr)
## basic example code
```
